---
output: html_document
---
## Homework 3

<!--
You can use the example3.Rmd or other files to find examples
of the codes you'll need to use to complete this assignment. I strongly
urge you to copy and paste relevant code that you know works from my
examples or instructions and then edit that code so you're working
with the appropriate variables for the homework.
-->

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->

<!--
Read in the homework3.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
-->
This is where I read in the data.
```{r}
dat<-read.csv("homework3.csv")
```


<!--
Check the structure of the data.
-->
This is where I checked the structure of the data.
```{r}
str(dat)
```


<!--
Find the mean, median, and standard deviation using the sd() function
for the overall level of conservatism.
-->
Here I will find the mean, median, and standard deviation for the level of conservatism.
```{r}
mean(dat$conservatism)
median(dat$conservatism)
sd(dat$conservatism)
```

The mean is 52.3, the median is 53.8, and the standard deviation is 19.6

<!--
Find the mean level of support for freshmen only.
-->
Here I will find the mean level of conservatism for Freshman only.
```{r}
mean(dat$conservatism[dat$year=="freshman"])
```
The mean level of conservatism for Freshman only is 47.5

<!--
Find the mean level of support for sophomore business students only.
-->
Here I will find the mean level of conservatism for Sophomore Business students only.
mean(dat$conservatism[dat$year=="sophomore" & dat$major=="business"])
```
The mean for this is 61.6