## Example 6

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->

<!--
Read in the homework6.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
The fabricated data are supposed to approximate how people perform
in different types of visual searches. Specifically, we're 
comparing performance in feature searches (e.g. looking for a red
X among green Xs) and conjunction searches (e.g. looking for a red
X among green Xs and red Os). We're also looking at how the number
of distractors within the search display effect our data.
-->
First, I will read in the data.
```{r}
dat<-read.csv("homework6.csv")
```


<!--
Check the structure of the data and change any variables that should
be factor variables into factor variables
-->
Next I must check the structure of the data.
```{r}
str(dat)
```
From the structure results, I see that distractors, subject, and subject2 must be changed to factors and I will do that next.
```{r}
dat$distractors<-as.factor(dat$distractors)
dat$subject<-as.factor(dat$subject)
dat$subject2<-as.factor(dat$subject2)
```

<!--
Perform a one-way between-subjects ANOVA examining for effects of 
the the number of distractors for the conjunction searches only.
Also create a line graph to help you interpret the results of your
analysis.
-->
Next, I must get the data from the conjunction searches only. 
```{r}
temp<-dat[dat$type=="conjunction",]
```
Next, I can run ANOVA. 

```{r}
summary(aov(rt~distractors, data=temp))
```
To interpret this data better, I'll create a line graph that shows the response time when the number of distractors is increased.

```{r}
library(ggplot2)
library(gplots)
library(dplyr)

temp<-dat%>%group_by(distractors)%>%
  summarize(means=mean(rt),
            sems=sd(rt)/sqrt(length(rt)))

f<-ggplot(temp, aes(x=as.factor(distractors),
                    y=means,
                    group=1))+
  geom_line(size=1)+
  geom_point(size=2)+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2)+
  ggtitle("Effect of Distractors")+
  labs(x="Number of Distractors",y="Response Time")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())
f
```

From the graph I can see that the response time increases as the number of distractors increases.
<!--
Perform a one-way within subjects ANOVA on the same data you analyzed
earlier. Tip: use subject as the subjects variable for this analysis.
-->
Now I will conduct a one way within subjects ANOVA.
Because I changed temp, I don't have the same data I analyzed last time, so I'm going to reuse the code I first used to create temp so I can perform the appropriate analysis.
```{r}
temp<-dat[dat$type=="conjunction",]
```
Now that I have my data from earlier, I can run the ANOVA.
```{r}
summary(aov(rt~distractors+
              Error(subject/distractors),data=temp))
```
As the number of distractors increased, they needed more time to respond, F(2,14)=56.5, p<.05
<!--
Perform a between-subjects ANOVA examining for the effects of and
interactions between the number of distractors and the search type.
Make sure to interpret your results.
-->
Next, I will perform a between-subjects ANOVA.
```{r}
summary(aov(rt~distractors*type, data=dat))
```
<!--
Create a line graph and a grouped bar graph to help us interpret
the results of the previous analyses. Include error bars in your
figures.
-->
In order to create a line graph I must first summarize the data.

```{r}
temp<-dat%>%group_by(distractors,type)%>%
  summarize(means=mean(rt),
            sems=sd(rt)/sqrt(length(n)))
```
<!--
Interpret the statistical results in light of the figures.
-->
Now I can create the figures.
```{r}
f<-ggplot(temp, aes(x=distractors,
                    y=means,
                    group=type,
                    color=type))+
  geom_line(size=1)+
  geom_point(size=2)+
  scale_color_manual(values=c("darkgreen","red"),
                     name="Type",
                     breaks=c("conjunction","feature"),
                     labels=c("conjunction", "feature"))+
  geom_errorbar(aes(ymax=means+sems, ymin=means-sems),width=.2)+
  ggtitle("Response Time Depending on Type and Number of Distractors")+
  labs(x="Number of Distractors",y="Response Time")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())+
  theme(legend.position=c(.2,.85))+
  theme(legend.background=element_blank())+
  theme(legend.background=element_rect(color="black"))+
  theme(legend.title=element_blank())+
  theme(legend.title=element_text(size=12))+
  theme(legend.title.align=.5)+
  theme(legend.text=element_text(size=10,face="bold"))
f

f<-ggplot(temp, aes(x=distractors,
                    y=means,
                    fill=type))+
  geom_bar(stat="identity",position=position_dodge())+
  scale_fill_manual(values=c("darkgreen","red"),
                     name="Type",
                     breaks=c("conjunction","feature"),
                     labels=c("conjunction", "feature"))+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2,
                position=position_dodge(.9))+
  ggtitle("Response Time dependent upon Type and Number of Distractions")+
  labs(x="Number of Distractors",y="Response Time")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())+
  theme(legend.position=c(.2,.86))+
  theme(legend.background=element_blank())+
  theme(legend.background=element_rect(color="black"))+
  theme(legend.title=element_blank())+
  theme(legend.title=element_text(size=12))+
  theme(legend.title.align=.5)+
  theme(legend.text=element_text(size=10,face="bold"))
f
```

This graph shows that as the number of distractors went up, so did the response time. The response times were also shorter for the feature type.
<!--
Perform a within-subjects two-way ANOVA examining for the effects
of and interactions between number of distractors and search type.
Tip: use subject as the subject's variable for this analysis.
Interpret the results of the analysis based on the statistical
results and your earlier figures.
-->
Here I'm performing a within-subjects two-way ANOVA to examine for the effects of and interactions between number of distractors and search type.

```{r}
summary(aov(rt~distractors*type+ 
               Error(subject/(distractors*type)),data=dat))
```
Based upon this summary analysis, we can see that number of distractors affected the participant's response time, F(2,14)=11.2, p=.0013. The participants in conjunction type needed significantly more time to respond. F(1,7)=1626, p< .05. Participants in the feature type decreased response time as the number of distractors increased, F(2,14)=32.1, p<.05
<!--
Finally conduct and interpret the results of a mixed ANOVA in which
number of distractors varies within subjects and the type of search
varies between subjects. Make sure to interpret your results. Tip:
use subject2 as your subject's variable for this analysis.
-->
Finally, I will conduct a  mixed ANOVA.
```{r}
summary(aov(rt~distractors*type+
              Error(subject2/distractors),
            data=dat))
```
From this analysis, we can see that type affects performance F(1,14)=182.4, p<.05 We can see that distractors affect the response time F(2,28)=10.99, p.<.05. There is also a interation between distractors and type F(2,28)=32.5, p.<.05.