## Homework 5

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->



<!--
Read in the homework5.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
The data are fabricated and include the number of words per minute
that people can type when listening to no music and when listening
to heavy metal.
-->
Here I read in the data.
```{r}
dat<-read.csv("homework5.csv")
```


<!--
Check the structure of the data.
-->
Next, I must check the structure of the data.
```{r}
str(dat)
```
You can see that dat has two variables: music and wpm

Here I will find the mean words per minute for the two groups.

<!--
Find the mean words per minute for the two groups.
-->
  
```{r}
mean(dat$wpm[dat$music=="metal"])
mean(dat$wpm[dat$music=="none"])
```

The mean for the metal group is 48.03665, and the mean for the none group is 42.44641. Therefore, we can see that the none group completed the task faster.

<!--
Run an independent t-test to determine if the mean wpm for the
no music group is different from the mean wpm from heavy metal
group. Interpret the results of your analysis after you run it.
-->

Now I'll run an independent t-test to see if my interpretation was correct.
```{r}
t.test(dat$wpm[dat$music=="metal"],
       dat$wpm[dat$music=="none"],
       var.equal=TRUE)
```
These results show that the none group performed the tasks faster than the metal.
<!--
Run another independent t-test with the alternative hypothesis that
the heavy metal group types faster than the no music group. Interpret
the results of your analyses.
-->
Now, I'll run an independent t-test with the alternative hypothesis that the experimental group is faster than the control group.

```{r}
t.test(dat$wpm[dat$music=="metal"],
       dat$wpm[dat$music=="none"],
       var.equal=TRUE,
       alternative="greater")
```


<!--
Create a bar graph of the data.
-->
In order to create a bar graph of the data, I need to load the ggplot2, gplots, and dplyr libraries.


install.packages("ggplot2")
install.packages("gplots")
install.packages("dplyr")

```{r}
library(ggplot2)
library(gplots)
library(dplyr)
```
Next I need to use dplyr to summarize the data and find the means and standard errors of the means for the different groups.

```{r}
temp<-dat%>%group_by(music)%>%
  summarize(means=mean(wpm), sems=sd(wpm)/sqrt(length(wpm)))
```

With this data, I can now make a graph.
```{r}
f<-ggplot(temp,aes(x=factor(music),y=means))+
  geom_bar(stat="identity", color="black",
           fill=c("deepskyblue2", "deeppink"))+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2)+
  ggtitle("Words per minute based on music")+
  labs(x="Music", y="Words Per Minute (wpm)")+
  scale_x_discrete(breaks=c("metal","none"),
                   labels=c("metal","none"))+
  theme(plot.title=element_text(size=15,
                                face="bold",
                                vjust=.5))+
  theme(axis.title.x=element_text(size=12,
                                  face="bold",
                                  vjust=-.25))+
  theme(axis.title.y=element_text(size=12,
                                  face="bold",
                                  vjust=.25))+
  theme(axis.text.x=element_text(size=10,
                                 face="bold",
                                 color="black"))+
  theme(axis.text.y=element_text(size=10,
                                 face="bold",
                                 color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),
        axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())
f
```
<!--
Conduct and interpret a two-tailed paired t-test on the data.
-->

Next, I will conduct and interpret a two-tailed paired t-test with the data.

```{r}
t.test(dat$wpm[dat$music=="metal"],
       dat$wpm[dat$music=="none"],
       var.equal=TRUE,
       paired=TRUE)
```
Individuals in the none condition completed the task more quickly than individuals in the metal condition.